---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# edbuildr

<!-- badges: start -->
<!-- badges: end -->

The goal of ```edbuildr``` is to import EdBuild's master dataset of school district finance,
  student demographics, and community economic indicators for every school district in the United States.  
  The master dataset is built from the US Census, Annual Survey of School System Finances (F33)
  and joins data from the National Center for Education Statistics, Common Core of Data (CCD);
  the US Census, Small Area Income and Poverty Estimates (SAIPE); and the US Census,
  Education Demographic and Geographic Estimates (EDGE). We apply EdBuild's standard processing to the
  dataset and provide the option to select from four different exclusion criteria - see the masterpull help
  file for full details. The master dataset is available for any school year from 2013 to 2018 or
  longitudinally for all years 2013-2018. School year is identified by the end year. For example, the 2017-18 school
  year is 2018. Additional functions in the package use EdBuild's master data to analyze the difference 
  between neighboring school districts and create formatted excel tables of school district data. For full
  details about EdBuild's data processing please see EdBuild (2020)
  <http://data.edbuild.org/>. 

## Installation

You can install the released version of edbuild from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("edbuildr")
```

## Example

To view school district finance data for all districts: 

```{r example}
library(edbuildr)
## To import EdBuild's master dataset of school district finance, student demographic, and community economic data for 2017:
master_18 <- masterpull(data_year = "2018")

str(master_18)
```

## Authors
* Megan Brodzik (meganbrodzik@gmail.com), maintainer
* Cecilia Depman (cecilia.depman@gmail.com), author 
* Sara Hodges (sara.hodges@gmail.com), author
* Kailey Spencer (kailey.spencer.depoe@gmail.com), contributor

